Project1_RM_Objective_1

### 2020-02-16 WorkingCode/Project1_RM_LL_Objective_1.2.16.20.Rmd
RM and LL code combined
Data set excludes neighbourhood_group=Staten Island

---
title: "Project1_RM_Objective_1"
Date: 2/10/2020
Author: Reagan Meagher
---

----------
  SETUP
----------

@@

```{r libraries}
library(tidyverse)
library(caret)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
```

----------
   EDA
----------

@@

>>>>

---
title: "Project1_RM_Objective_1"
Date: 2/16/2020
Author: "Reagan Meagher and Laura Lazarescou"
Output: "html"
---

# ----------
##  SETUP
# ----------

@@

```{r libraries}
library(tidyverse)
library(caret)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
library(glmnet)
```

# ----------
##   EDA
# ----------

@@

## Begin Ridge, LASSO, Elastic Net Analysis

```{r }

## Ridge, LASSO and Elastic Net Regression and Regularization
## Source:

# https://hackernoon.com/an-introduction-to-ridge-lasso-and-elastic-net-regression-cca60b4b934f

# library(tidyverse) # all included in top of file library statements
# library(caret)
# library(glmnet)

# Using train and test datasets created above

# Format Predictors for glmnet() train  (linear and log(price))

x <- model.matrix(price~., linear.train)[,-1]
xlog <- model.matrix(lprice~., log.train)[,-1]

# Format responses for glmnet() train (linear and log(price))

y <- linear.train$price
ylog <- log.train$lprice

```

## Linear-Linear Ridge Regularization, glmnet() alpha=0

```{r Ridge}
# Performing Ridge regression
# As we mentioned in the previous sections, lambda values have a large effect on coefficients so now we will compute and choose a suitable one.
# Then we perform a cross validation with the lambda value corresponding to the lowest prediction error before fitting the data to the model and viewing the coefficients.

cv.r <- cv.glmnet(x, y, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
cv.r$lambda.min
model.ridge <- glmnet(x, y, alpha = 0, lambda = cv.r$lambda.min)
coef(model.ridge)
plot(cv.r)

## Test Linear Ridge Model for Accuracy, RMSE and R-squared

x.test.ridge <- model.matrix(price ~., linear.test)[,-1]
predictions.ridge <- model.ridge %>% predict(x.test.ridge) %>% as.vector()
data.frame(RMSE.r = RMSE(predictions.ridge, linear.test$price),Rsquare.r = R2(predictions.ridge, linear.test$price))
```

## Log-Linear Ridge Regularization, glmnet() alpha=0

```{r Log-Ridge}
# Performing Log-Linear Ridge regression

cv.r <- cv.glmnet(xlog, ylog, alpha = 0) # alpha=0 is Ridge Regularization, choose minimum lambda
cv.r$lambda.min
model.ridgeL <- glmnet(xlog, ylog, alpha = 0, lambda = cv.r$lambda.min)
coef(model.ridgeL)
plot(cv.r)

## Test Log-Linear Ridge Model for Accuracy, RMSE and R-squared

xlog.test.ridge <- model.matrix(lprice ~., log.test)[,-1]
log.predictions.ridge <- model.ridgeL %>% predict(xlog.test.ridge) %>% as.vector()
data.frame(RMSE.r = RMSE(log.predictions.ridge, log.test$lprice),Rsquare.r=R2(log.predictions.ridge, log.test$lprice))
```
## Linear-Linear LASSO Regularization, glmnet() alpha=1

```{r Linear LASSO}

cv.L <- cv.glmnet(x, y, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
cv.L$lambda.min
model.lasso <- glmnet(x, y, alpha = 1, lambda = cv.L$lambda.min)
coef(model.lasso)
plot(cv.L)

## Test Linear LASSO Model for Accuracy, RMSE and R-squared

x.test.lasso <- model.matrix(price ~., linear.test)[,-1]
predictions.lasso <- model.lasso %>% predict(x.test.lasso) %>% as.vector()
data.frame(RMSE.r = RMSE(predictions.lasso, linear.test$price),Rsquare.r = R2(predictions.lasso, linear.test$price))
```

## Log-Linear LASSO Regression, glmnet() alpha=1

```{r Log-LASSO}
# Performing Log-Linear LASSO regression

cv.r <- cv.glmnet(xlog, ylog, alpha = 1) # alpha=1 is LASSO Regularization, choose minimum lambda
cv.r$lambda.min
model.lassoL <- glmnet(xlog, ylog, alpha = 1, lambda = cv.r$lambda.min)
coef(model.lassoL)
plot(cv.r)

## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared

xlog.test.lasso <- model.matrix(lprice ~., log.test)[,-1]
log.predictions.lasso <- model.lassoL %>% predict(xlog.test.lasso) %>% as.vector()
data.frame(RMSE.r = RMSE(log.predictions.lasso, log.test$lprice),Rsquare.r=R2(log.predictions.lasso, log.test$lprice))
```

## Linear-Linear Elastic Net Regression, selecting alpha=.5

```{r elastic net}

cv.EN <- cv.glmnet(x, y, alpha = .5) # alpha=.5 is a chosen value between 0 and 1
cv.EN$lambda.min
model.elasticnet <- glmnet(x, y, alpha = .5, lambda = cv.EN$lambda.min)
coef(model.elasticnet)
plot(cv.EN)

## Test Linear Elastic Net Model for Accuracy, RMSE and R-squared

x.test.elasticnet <- model.matrix(price ~., linear.test)[,-1]
predictions.elasticnet <- model.elasticnet %>% predict(x.test.elasticnet) %>% as.vector()
data.frame(RMSE.r = RMSE(predictions.elasticnet, linear.test$price),Rsquare.r = R2(predictions.elasticnet, linear.test$price))
```
## Log-Linear Elastic Net Regression, selecting alpha=.1

```{r Log-Elastic Net}
# Performing Log-Linear Elastic Net regression

cv.r <- cv.glmnet(xlog, ylog, alpha = .1) # alpha=.1 is chosen value for Elastic Net Regularization, choose minimum lambda
cv.r$lambda.min
model.ENL <- glmnet(xlog, ylog, alpha = .1, lambda = cv.r$lambda.min)
coef(model.ENL)
plot(cv.r)

## Test Log-Linear LASSO Model for Accuracy, RMSE and R-squared

xlog.test.EN <- model.matrix(lprice ~., log.test)[,-1]
log.predictions.EN <- model.ENL %>% predict(xlog.test.EN) %>% as.vector()
data.frame(RMSE.r = RMSE(log.predictions.EN, log.test$lprice),Rsquare.r=R2(log.predictions.EN, log.test$lprice))
```
